%-------------------------
% Resume in LateX
% Author : Sandeep Reddy
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubSubItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sandeep Reddy Thathireddy}} & Email: \href{mailto:thathireddysandeepreddy05@gmail.com}{thathireddysandeepreddy05@gmail.com}\\
  \href{https://linkedin.com/in/sandeepreddythathireddy}{LinkedIn} & Mobile: \href{tel:+817044836964}{+81-704-483-6964} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Indore}{Indore, Madhya Pradesh}
      {Bachelor of Technology in Electrical Engineering; CGPA: 8.62/10.0}{Jul 2018 -- May 2022}
    % \resumeSubheading
    %   {Birla Institute of Technology and Science}{Pilani, India}
    %   {Bachelor of Engineering in Electrical and Electronics; GPA: 3.66 (9.15/10.0)}{Aug 2008 -- July 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rakuten}{Tokyo, Japan}
      {Senior Software Engineer}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Technologies}
          {Java, SpringBoot, SQL, JUnit, JMockit, Karate, JavaScript, Jest, Cypress, AWS, Splunk, Jenkins}
        \resumeItem{PayVault \& PayStep (PVPSG)}
          {Secure payment platform handling credit card storage, tokenization, and a merchant checkout page supporting multiple payment options (Card, PayPal, PostPay, AliPay, etc.).}
      \resumeItemListEnd
   \textbf{\small Key Achievements}
   \resumeSubSubheading
    {PayStep}{Backend}
    \resumeItemListStart
      \resumeSubSubItem
        {Successfully led Java 17 to 21 migration and implemented TransactionGuard — a protective transaction feature that significantly reduced payment friction and improved overall transaction reliability.}
      \resumeSubSubItem
        {Decoupled application and batch logic into separate modules (common, app, batch), improving release efficiency and maintainability in an Agile environment.}  
    \resumeItemListEnd
  \resumeSubSubheading
    {PayVault JS}{Frontend}
    \resumeItemListStart
    \resumeSubSubItem
        {Built the new Customer\_PV\_JS product from scratch, based on the existing PayVault\_JS\_v7 codebase. This product is tailored exclusively for external clients (non-Rakuten).}
    \resumeSubSubItem
        {Key improvements over PayVault\_JS\_v7 include enhanced logging for attack monitoring and debugging, a cleaner and more maintainable codebase, significantly expanded unit test coverage, and newly added integration tests.}
    \resumeItemListEnd

      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {Accenture}{Tokyo, Japan}
      {Software Engineer}{Nov 2022 -- May 2025}
      \resumeItemListStart
        \resumeItem{Technologies}
          {Java, Spring, SQL, Angular, TypeScript, Jenkins}
        \resumeItem{Global Billing System (GBS)}
          {Billing platform enabling users to manage invoices, while internal teams access audit reports and billing summaries. Payment processing was handled by a separate team.}
      \resumeItemListEnd
      \textbf{\small Key Achievements}
      \resumeSubSubheading
        {GBS}{Backend}
      \resumeItemListStart
        \resumeSubSubItem
          {Optimized batch processing systems, achieving a 30\% reduction in processing time, significantly improving operational efficiency.}
        \resumeSubSubItem
          {Enhanced application scalability and maintainability by implementing effective exception handling techniques, resulting in a 20\% reduction in errors through improved logging.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------CORE RESPONSIBILITIES---------------  
\section{Core Responsibilities}
  \resumeSubHeadingListStart
    \resumeSubSubItem
      {Cross-functional team collaboration, full SDLC, code reviews, mentoring junior developers.}
  \resumeSubHeadingListEnd    

%--------SKILLS------------
\section{Skills}
  \textbf{\small Technical Skills}
    \resumeItemListStart
      \resumeItem{Back-End Development}
        {Java, SpringBoot, SQL, JUnit, JMockit, Karate.}
      \resumeItem{Front-End Development}
        {JavaScript, Angular, TypeScript, Jest, Cypress, HTML, CSS.}
      \resumeItem{Deployment, Tools}
        {AWS, Splunk, Jenkins, Git.}
    \resumeItemListEnd
  % \textbf{\small Soft Skills:}{Teamwork, Communication, Adaptability, Time Management, Delivering Results, Continuous Learning.}
    % \resumeItemListStart
    %   \item
    %     {Teamwork, Communication, Adaptability, Time Management, Delivering Results, Continuous Learning.}
    % \resumeItemListEnd    

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Restaurant App Food Delivery}{\href{https://github.com/Sandeep-may/restaurant-app}{GitHub}}
      {React Native, Node.js, PostgreSQL, Docker, OCI}{}
        \resumeItemListStart
          \resumeSubSubItem
            {Architected and developed a production-scale monorepo for a restaurant MVP, featuring a React Native mobile client and a Node.js/Express REST API.}
          \resumeSubSubItem  
            {Containerized the backend using Docker and Docker Compose, streamlining deployment to OCI with PostgreSQL and automated Prisma migrations. Engineered robust middleware for CORS, logging (Morgan), and centralized error handling, ensuring a scalable and maintainable codebase.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
